How to \emph{not} write Virtual Machines for Dynamic Languages

### 2007-07-24 talk/dyla2007/talk.tex
Typo - details.

\begin{frame}
  \frametitle{Benefits of implementing on top of OO VMs}
  \begin{itemize}
  \item
    higher level of implementation
  \item
    the VM supplies a GC and mostly a JIT
  \item
    better interoperability than what the C level provides
  \item
    some proponents believe that eventually one single VM should be enough
  \end{itemize}
  \pause
  \begin{block}{
    Python Case}
    \begin{itemize}
    \item
      both Jython and IronPython allow easy access to the underlying VMs libraries
    \item
      XXX what else?
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}
  \frametitle{The problems of OO VMs}
  \begin{itemize}
  \item
    some of the benefits of OO VMs don't work out in practice
  \item
    most immediate problem: it be hard to map concepts of the dynamic lang to
    the host OO VM
  \item
    performance is often not improved, and can be very bad, because of the
    semantic mismatch between the dynamic language and the host VM
  \item
    poor interoperability with everything outside the OO VM
  \item
    in practice, one OO VM is not enough
  \end{itemize}
  \pause
  \begin{block}{
    Python Case}
    \begin{itemize}
    \item
      Jython about 5 times slower than CPython
    \item
      IronPython is about as fast as CPython (but some introspection features
      missing)
    \item
      XXX something about semantic mismatch?
    \end{itemize}
  \end{block}

>>>>

\begin{frame}
  \frametitle{Benefits of implementing on top of OO VMs}
  \begin{itemize}
  \item
    higher level of implementation
  \item
    the VM supplies a GC and mostly a JIT
  \item
    better interoperability than what the C level provides
  \item
    some proponents believe that eventually one single VM should be enough
  \end{itemize}
  \pause
  \begin{block}{
    Python Case}
    \begin{itemize}
    \item
      both Jython and IronPython integrate well with their host OO VM
    \item
      XXX what else?
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}
  \frametitle{The problems of OO VMs}
  \begin{itemize}
  \item
    some of the benefits of OO VMs don't work out in practice
  \item
    most immediate problem: it can be hard to map
    concepts of the dynamic lang to
    the host OO VM
  \item
    performance is often not improved, and can be very bad, because of the
    semantic mismatch between the dynamic language and the host VM
  \item
    poor interoperability with everything outside the OO VM
  \item
    in practice, one OO VM is not enough
  \end{itemize}
  \pause
  \begin{block}{
    Python Case}
    \begin{itemize}
    \item
      Jython about 5 times slower than CPython
    \item
      IronPython is about as fast as CPython (but some introspection features
      missing)
    \item
      XXX something about semantic mismatch?
    \end{itemize}
  \end{block}
